\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-07 lang-design.tex
overriding

>>>>

In an OO language, a subclass can override methods of a superclass.
Similar expressiveness is useful for metatheory mechanization, too.
%
For example, in a derived family, the programmer may want to override
a lemma that was proved by induction in the base family,
by a new proof that uses a different proof strategy.

Coq distinguishes \emph{opaque} definitions from \emph{transparent} ones.
Our plugin supports the overriding of opaque definitions, which
include most proofs.
It is safe to override opaque definitions, because Coq will never attempt to unfold them.
For transparent definitions, the common case is that the programmer does
not want to override them.
In \cref{fig:stlc-mechanized}, "env", "empty", "subst", and "steps" are
transparent---that is, they are not defined with \lsti{Qed}---and thus
the plugin treats them as non-overridable by default.
As a result, the definitional equalities on "env", "empty", and "steps",
as well as the propositional equality on "subst", are available to the
type checker for type-checking the families.

Our plugin does allow the overriding of transparent definitions that are
explicitly marked as \lsti{Overridable} by the programmer.
Overriding is made safe by requiring that when an overridable field is
overridden, code whose type checking requires unfolding that definition
should be overridden too.
We give an example in a supplemental appendix.
